CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-08 paper.Rmd
Comment the pipeline command

```{r}
# Available on CRAN
library(targets)

# Available from MatthewHeun on GitHub
# with devtools::install_github("MatthewHeun/xxxxxx")
# library(IEATools)

# Available from EnergyEconomyDecoupling on GitHub
# with devtools::install_github("EnergyEconomyDecoupling/xxxxxx")
# library(PFUPipelineTools)
library(PFUSetup)

# Run the PFUDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))

>>>>

```{r}
library(targets)
# Run the PFUDatabase pipeline
# targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))
